### 2019-08-22 abstract.tex
Version 3.0

\begin{abstract}
The Transit Monitoring in the South (TraMoS) project aims to perform photometric follow-up in known transiting exoplanets. This process provides not only essential information about the transiting planet but also about their planetary system's architecture. Departures from the linear ephemeris given by Keplerian motion, the so-called Transit Timing Variations (TTV), can only be spotted through extensive follow-up, and could suggest the existence of additional bodies in the system, such as planetary companions or exomoons.

This Master thesis recapitulates the last years of the TraMoS project, on which new targets were selected, modern tools were used and new analysis were performed. I studied 27 new light curves of three hot Jupiters: WASP-18b, WASP-19b, and WASP-77Ab. Their orbital and physical parameters were refined, and their linear ephemeris updated thanks to the inclusion of archival transit time data. Given the lack of significant variations in their transit times, dynamical analysis can place upper mass limits in hypothetical pertubers. Bodies with masses greater than $50\,M_{\odot}$ can be discarded for WASP-18b, $6\,M_{\odot}$ for WASP-19b, and $10\,M_{\odot}$ for WASP-77Ab. Furthermore, I included recent TESS data for the three targets, supporting the linear ephemeris as the best fit for their transit times

The results presented in this thesis support the rare occurrence  of companions in hot Jupiters systems. Further studies may confirm if this kind of planet goes through a different formation process ending up orbiting alone on their systems or they have very small and unseen companions.
\end{abstract}

>>>>

\begin{abstract}
The Transit Monitoring in the South (TraMoS) project aims to perform photometric follow-up in known transiting exoplanets. This process provides not only essential information about the transiting planet but also about their planetary system's architecture. Departures from the linear ephemeris given by Keplerian motion, the so-called Transit Timing Variations (TTV), can only be spotted through extensive follow-up and could suggest the existence of additional bodies in the system, such as planetary companions or exomoons.

This Master thesis recapitulates the last years of the TraMoS project, on which new targets were selected, modern tools were used and new analysis was performed. I studied 27 new light curves of three hot Jupiters: WASP-18b, WASP-19b, and WASP-77Ab. Their orbital and physical parameters were refined, and their linear ephemeris updated thanks to the inclusion of archival transit time data. Given the lack of significant variations in their transit times, dynamical analysis can place upper mass limits in hypothetical perturbers. Bodies with masses greater than $50\,M_{\odot}$ can be discarded for WASP-18b, $6\,M_{\odot}$ for WASP-19b, and $10\,M_{\odot}$ for WASP-77Ab. Furthermore, I included recent TESS data for the three targets, supporting the linear ephemeris as the best fit for their transit times

The results presented in this thesis support the rare occurrence of companions in hot Jupiters systems. Further studies may confirm if this kind of planet goes through a different formation process ending up orbiting alone on their systems or they have very small and unseen companions.

\end{abstract}

### 2019-08-22 conclusion.tex
Version 3.0

During this Master project, I studied three exoplanets: WASP-18b, WASP-19b, and WASP-77Ab. For these targets, I analyzed a total of twenty-six new light curves: eight of WASP-18b, nine of WASP-19b and nine of WASP-77Ab. In the case of WASP-77Ab, four light curves were taken from the Exoplanet Transit Database (ETD)\footnote{\url{var2.astro.cz/ETD}} to obtain a wider time coverage. For the light curves coming from the TraMoS project, I started from performing aperture photometry of the targets using our data reduction pipeline (for further details see \ref{chap:pipeline}), in order to obtain high-precision light curves. Then, I used EXOFASTv2 \cite{Eastman2013,Eastman2017} to get the best fit for the light curve's data and hence, to refine their orbital and physical parameters and obtain their transit times.

>>>>

During this Master project, I studied three exoplanets: WASP-18b, WASP-19b, and WASP-77Ab. For these targets, I analyzed a total of twenty-six new light curves: eight of WASP-18b, nine of WASP-19b and nine of WASP-77Ab. In the case of WASP-77Ab, four light curves were taken from the Exoplanet Transit Database (ETD)\footnote{\url{var2.astro.cz/ETD}} to obtain a wider time coverage. For the light curves coming from the TraMoS project, I started from performing aperture photometry of the targets using our data reduction pipeline (for further details see \ref{chap:pipeline}), to obtain high-precision light curves. Then, I used EXOFASTv2 \cite{Eastman2013,Eastman2017} to get the best fit for the light curve's data and hence, to refine their orbital and physical parameters and obtain their transit times.

### 2019-08-22 introduction.tex
Version 3.0

\chapter{Introduction}\label{chap:intro}
The idea of the existence of planets orbiting other stars different from our Sun lived in the human imagination for centuries. During the sixteenth century, the Italian philosopher Giordano Bruno suggested, for the first time in history, that more planets could be outside the Solar System. Even though the first claims of exoplanet detection began at the end of the nineteenth century, it was not until more than four hundred years after Bruno's statement, that the first exoplanet was confirmed in 1992. Surprisingly, it was not just one exoplanet but three, orbiting the pulsar PSR B1257+12 more than 1000 light-years away from us. Today, more than 4,000 exoplanets are confirmed, and thousands more are waiting for their confirmation.

%cita del sixteenth century
%frases sobre otros métodos

@@

The discovery of three exoplanets orbiting the pulsar PSR B1257+12 is still very rare. The technique used to find them is called Pulsar Timing and it consists in measuring the variation of a pulsar's pulsation period due to the presence of a body orbiting it. As pulsars are not very common and we know that planet may be orbiting main sequence stars -- as the Earth and all the Solar System --, the latter become the principal target on which the hunting of exoplanet is dedicated. Planets are small when compare to their host star, that is why most of the current discovery techniques are focus in observing the effects in the stars, or how what we observed from them changed, caused by the presence of planets. Nevertheless, Direct Imaging is the only technique on which the planet is observed directly but the star needs to be covered to only received the thermal emission produced by the planet.

Microlensing is different from all the other discovery techniques, because a third, bright background star is required to obtain the desire effect: a gravitational lensing is produced by the star with a planet (multiple lens). As the primary lens is small -- around $1\,M_{odot}$ -- the two images produced by the gravitational lensing are very close between each other and the event can not be resolved. The presence of a planet will cause a deviation in the magnification curve of the event. In the other hand, Astrometry measurements can be use to discover exoplanets too. With the current high-precision in the position of the stars, even their displacement in the sky can be detected. Similar to the Radial Velocity technique, through Astrometry the displacement of the star due to the gravity of a planet can be measure.

The two techniques that have contributed the most to the discovery of extrasolar planets are Radial Velocity and Transits (see Figure \ref{exoplanets}). Each one of these techniques had their own advantages depending on the physical properties of the planetary system. When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases, proportionally to the radius of the planet. Thus, the radius ratio between the planet and the star, $R_{p}/R_{*}$ can be determined directly using the Transit method. In the other hand, the gravity due to the presence of a planet will set the center of mass of the system, in a place different from the star's center. Therefore, the star will move in its own small orbit with a radius proportional to the mass of the planet. In this case, the Radial Velocity method unveils the planet's minimum mass ($M_{p}\sin i$).

Anyway, the rising research field of exoplanets does not end with their discovery. Performing follow-up and proper characterization of discovered exoplanets is essential to obtain a full list of orbital and planetary parameters. For instance,  39\%  of the total number of discovered exoplanets have a proper measurement of their masses, and only 17\% have their mass and radius computed\footnote{c.f. NASA Exoplanet Archive Database.}.

@@

The perfect scenario comes when both methods, Transits and Radial Velocity, can be used in the same planetary system, allowing to derive essential properties of the planet. Combining Transits and Radial Velocity follow-up the whole system can be characterize. From Transits we get the orbital inclination, then the real mass can be computed with Radial Velocity measurements. From Transits we get the radius ratio of the system, assuming that the star is previously well characterized, the radius of the planet is derived. Then, as we already have the mass of the planet, the mean density can be estimated. This parameter gives a clue of the possible composition of the planet. Moreover, if the follow-up is performed combining Transits with big telescopes, for instance the Very Large Telescope, important information about the planet can be unveiled, even their atmospheric composition and dynamics.

@@

Continued photometric monitoring not only increased precision of planetary parameters but provides potential information about the planet and its environment. Through the continued 
 Variations in the transit timing -- when the planet passes in front of its star -- could be induced by companions gravitationally bounded, such as other planets in their systems or even exomoons \citep{Kipping2009a,Kipping2009b}. As most of the space mission have strict fields of view, performing photometric follow-up with ground-based telescopes is crucial to reveal important features of their systems. The Transit Timing Variation (TTV) technique \citep{Holman2005,Agol2005} is an efficient and powerful tool to detect small, unseen companions of already discovered exoplanets (see Figure \ref{exoplanets}). Kepler provided the firsts breakthrough discoveries of exoplanets showing TTV \citep{Holman2010}, and after the mission ended some projects started aiming to complete its legacy searching for TTVs. The Transit Monitoring in the South project (TraMoS) is one of its kind in the southern hemisphere, aiming to detect multi-exoplanetary systems trough the TTV method.

@@

This thesis is organized as follows: Chapter \ref{chap:tramos} summarizes the TraMoS project, its goals, techniques and achievements to date. Also, this chapter includes what we can learn from transit exoplanets' light curves and Transit Timing Variations. Chapter \ref{chap:paper} shows the analysis and results of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab, including  their observations and data reduction, light curve and RV analysis, measurements of TTVs and upper mass limit for possible companions in their systems. Then, Chapter \ref{chap:tess}  recapitulates the current stage of the TraMoS project on which TESS data is being incorporated. Here, I re-analyze the TTV curves of the previous targets WASP-18b, WASP-19b, and WASP-77Ab with new light curves from TESS. Finally, Chapter \ref{chap:conclusion} contains a summary of this thesis as well as some ideas for future work. The Appendix section includes a brief description of the aperture photometry pipeline utilized, all the Python scripts used to generate each light curve, and an example of the PDF file obtained after the aperture photometry procedure.

>>>>

\chapter{Introduction}\label{chap:intro}
The idea of the existence of planets orbiting other stars different from our Sun lived in the human imagination for centuries. During the sixteenth century, the Italian philosopher Giordano Bruno suggested, for the first time in history, that more planets could be outside the Solar System. Even though the first claims of exoplanet detection began at the begin of the twentieth century\footnote{The van Maanen 2 star, which later was confirmed as a white dwarf.}, it was not until more than four hundred years after Bruno's statement, that the first exoplanet was confirmed in 1992. Surprisingly, it was not just one exoplanet but three, orbiting the pulsar PSR B1257+12 more than 1000 light-years away from us. Today, more than 4,000 exoplanets are confirmed, and thousands more are waiting for their confirmation.

@@

The discovery of three exoplanets orbiting the pulsar PSR B1257+12 is still very rare. The technique used to find them is called Pulsar Timing and it consists in measuring the variation of a pulsar's pulsation period due to the presence of a body orbiting it. As pulsars are not very common and we know that planet may be orbiting main-sequence stars -- as the Earth and all the Solar System --, the latter become the principal target on which the hunting of exoplanet is dedicated. Planets are small when compare to their host star, that is why most of the current discovery techniques are focused on observing the effects in the stars, or how what we observed from them changed, caused by the presence of planets. Nevertheless, Direct Imaging is the only technique in which the planet is observed directly but the star needs to be covered to only received the thermal emission produced by the planet.

Microlensing is different from all the other discovery techniques because a third, bright background star is required to obtain the desired effect: gravitational lensing produced by the star with a planet (multiple lenses). As the primary lens is small -- around $1\,M_{\odot}$ -- the two images produced by the gravitational lensing are very close between each other and the event can not be resolved. The presence of a planet will cause a deviation in the magnification curve of the event. On the other hand, Astrometry measurements can be used to discover exoplanets too. With the current high-precision in the position of the stars, even their displacement in the sky can be detected. Similar to the Radial Velocity technique, through Astrometry the displacement of the star due to the gravity of a planet is measured.

The two techniques that have contributed the most to the discovery of extrasolar planets are Radial Velocity and Transits (see Figure \ref{exoplanets}). Each one of these techniques had their own advantages depending on the physical properties of the planetary system. When the orbit of the exoplanet is aligned with the line of sight from Earth, the pass of the planet in front of its host star causes that the star's flux decreases, proportionally to the radius of the planet. Thus, the radius ratio between the planet and the star, $R_{p}/R_{*}$ can be determined directly using the Transit method. On the other hand, the gravity due to the presence of a planet will set the center of mass of the system, in a place different from the star's center. Therefore, the star will move in its own small orbit with a radius proportional to the mass of the planet. In this case, the Radial Velocity method unveils the planet's minimum mass $M_{p}\sin i$.

Anyway, the rising research field of exoplanets does not end with their discovery. Performing follow-up and proper characterization of discovered exoplanets are essential to obtain a full list of orbital and planetary parameters. For instance,  39\%  of the total number of discovered exoplanets have a proper measurement of their masses, and only 17\% have their mass and radius computed\footnote{Information obtained from the NASA Exoplanet Archive Database \url{exoplanetarchive.ipac.caltech.edu}}.

@@

The perfect scenario comes when both methods, Transits and Radial Velocity, can be used in the same planetary system, allowing to derive essential properties of the planet. Combining Transits and Radial Velocity follow-up the whole system can be characterized. From Transits we get the orbital inclination, then the real mass can be computed with Radial Velocity measurements. From Transits we get the radius ratio of the system, assuming that the star is previously well characterized, the radius of the planet is derived. Then, as we already have the mass of the planet, the mean density can be estimated. This parameter gives a clue about the possible composition of the planet. Moreover, if the follow-up is performed combining Transits with big telescopes, for instance, the Very Large Telescope, important information about the planet can be unveiled, even their atmospheric composition and dynamics.

@@

Continued photometric monitoring not only increased the precision of planetary parameters but provides potential information about the planet and its environment. Through the observation of transit events during several epochs, variability in the planetary system can be detected. For instance, the first measurement of two planets gravitationally bounded was made by \citep{Holman2010}, this discovery was made thanks to the continued observations performed by the Kepler mission. This phenomenon is detectable observing during several epochs just one of the planets involved and analyzing how the presence of a companion produces such variability. Moreover, variability in transiting exoplanets -- specifically in the time of the transit -- can be attributed not only to planetary companions, but exomoons\citep{Kipping2009a,Kipping2009b}, tidal orbital decay\citep{Hoyer2016,Hoyer2016b}, secular orbits changes\citep{Adams2006} or relativistic effects \citep{Heyl2007}, among others.

The Transit Monitoring in the South project (TraMoS) is one of its kind in the southern hemisphere, aiming to detect multi-exoplanetary systems trough the variability in transit parameters of transiting exoplanets. To achieve this goal, extensive photometric follow-up of transiting exoplanets is being carry-on, using one-meter class telescopes located in Chile.

% Variations in the transit timing -- when the planet passes in front of its star -- could be induced by companions gravitationally bounded, such as other planets in their systems or even exomoons \citep{Kipping2009a,Kipping2009b}. As most of the space mission have strict fields of view, performing photometric follow-up with ground-based telescopes is crucial to reveal important features of their systems. The Transit Timing Variation (TTV) technique \citep{Holman2005,Agol2005} is an efficient and powerful tool to detect small, unseen companions of already discovered exoplanets (see Figure \ref{exoplanets}). Kepler provided the firsts breakthrough discoveries of exoplanets showing TTV \citep{Holman2010}, and after the mission ended some projects started aiming to complete its legacy searching for TTVs. The Transit Monitoring in the South project (TraMoS) is one of its kind in the southern hemisphere, aiming to detect multi-exoplanetary systems trough the TTV method.

@@

This thesis is organized as follows: Chapter \ref{chap:tramos} summarizes the TraMoS project, its goals, techniques, and achievements to date. Also, this chapter includes what we can learn from transit exoplanets' light curves and Transit Timing Variations. Chapter \ref{chap:paper} shows the analysis and results of the hot Jupiters WASP-18b, WASP-19b, and WASP-77Ab, including their observations and data reduction, light curve and RV analysis, measurements of TTVs and an upper mass limit for possible companions in their systems. Then, Chapter \ref{chap:tess}  recapitulates the current stage of the TraMoS project on which TESS data is being incorporated. Here, I re-analyze the TTV curves of the previous targets WASP-18b, WASP-19b, and WASP-77Ab with new light curves from TESS. Finally, Chapter \ref{chap:conclusion} contains a summary of this thesis as well as some ideas for future work. The Appendix section includes a brief description of the aperture photometry pipeline utilized, all the Python scripts used to generate each light curve, and an example of the PDF file obtained after the aperture photometry procedure.

### 2019-08-22 pipeline.tex
Version 3.0

Since the beginning of the TraMoS project, an aperture photometry pipeline has been in development, on which several graduate and undergraduates students worked and are currently working on it. This pipeline is Python-based and includes standard procedures of reduction, calibrations and aperture photometry, including bias and flat field corrections. The user needs to give the coordinates of the target and reference stars and a range of pixels for a possible aperture. Then, in order to produce high-precision light curves of the target and reference stars, the pipeline semi-automatic finds the best aperture and ring size, for the sky that produces the less RMS in the light curves.

The pipeline works with a specific directories' structure where all the needed information should be:
\begin{itemize}
\item raw: Folder containing the raw data of the observations. It could be fits files or compressed fits (e.g \textit{fit.ZIP}).
\item calib: This folder should include the flats -- sky or dome -- and bias files.
\item data: Empty folder which will contain the output data after the aperture photometry procedure.
\item figures: Empty folder on which all the figures generated in the reduction process will be store.
\item log: Folder containing the Python script to run the pipeline for the specific data set.
\item extraction.tex: Latex file which generates the PDF file with all the important information related to the aperture photometry procedure process, such as images of the stamps, radial profile of the target star, FWHM plots, preview of the light curve, etc.
\item tramos\_custom.sty: Customizable file containing the information related to the telescope, target's name, filter, date of the observation, RA, DEC and target's magnitude. When the pipeline finishes, it fills this file with the best aperture size obtained.
\end{itemize}

I have implemented dictionaries to ease the use of the pipeline with different telescopes. One of the biggest problems that I faced when I started reducing data, was the distinctness between the headers produced from different telescopes. For example, while some of them recorded the type of filter as \textit{FILTER}, other use could use \textit{FILTERB}. Also, as the TraMoS project has been collecting data since more than 10 year ago, some of our used telescopes were updated with new CCDs, producing that the pipeline were not longer functional. Currently, the pipeline works with data from the following telescopes: 
\begin{itemize}
\item La Silla Observatory: Danish 1.54 m (previous and after 2017) and REM.
\item Cerro Tololo Inter-American Observatory: SMARTS 0.9 m and 1 m.
\item Las Campanas Observatory: Warsaw, Swope, Du Pont.
\item Cerro Pachón: SOAR
\end{itemize}

>>>>

Since the beginning of the TraMoS project, an aperture photometry pipeline has been in development, on which several graduates and undergraduates students worked and are currently working on it. This pipeline is Python-based and includes standard procedures of reduction, calibrations, and aperture photometry, including bias and flat-field corrections. The user needs to give the coordinates of the target and reference stars and a range of pixels for a possible aperture. Then, to produce high-precision light curves of the target and reference stars, the pipeline semi-automatic finds the best aperture and ring size, for the sky that produces the less RMS in the light curves.

The pipeline works with a specific directories' structure where all the needed information should be:
\begin{itemize}
\item raw: Folder containing the raw data of the observations. It could be fits files or compressed fits (e.g \textit{fit.ZIP}).
\item calib: This folder should include the flats -- sky or dome -- and bias files.
\item data: Empty folder which will contain the output data after the aperture photometry procedure.
\item figures: Empty folder on which all the figures generated in the reduction process will be stored.
\item log: Folder containing the Python script to run the pipeline for the specific data set.
\item extraction.tex: Latex file which generates the PDF file with all the important information related to the aperture photometry procedure process, such as images of the stamps, the radial profile of the target star, FWHM plots, preview of the light curve, etc.
\item tramos\_custom.sty: A customizable file containing the information related to the telescope, target's name, filter, date of the observation, RA, DEC and target's magnitude. When the pipeline finishes, it fills this file with the best aperture size obtained.
\end{itemize}

I have implemented dictionaries to ease the use of the pipeline with different telescopes. One of the biggest problems that I faced when I started reducing data, was the distinctness between the headers produced from different telescopes. For example, while some of them recorded the type of filter as \textit{FILTER}, others use \textit{FILTERB}. Also, as the TraMoS project has been collecting data for more than 10 years ago, some of our used telescopes were updated with new CCDs, producing that the pipeline was no longer functional. Currently, the pipeline works with data from the following telescopes: 
\begin{itemize}
\item La Silla Observatory: Danish 1.54 m (previous and after 2017) and REM.
\item Cerro Tololo Inter-American Observatory: SMARTS 0.9 m and 1 m.
\item Las Campanas Observatory: Warsaw, Swope, Du Pont.
\item Cerro Pachón: SOAR
\end{itemize}

### 2019-08-22 tess.tex
Version 3.0

With the end of the Kepler mission, thousands of possible exoplanets remain as candidates known as Kepler Objects of Interest (KOI). The Kepler Object of Interest Network (KOINet: \citep{vonEssen2018,Freuddenthal2018}) in the Northern hemisphere, is a network of ground-based telescopes performing photometric follow-up of KOIs to continue what Kepler left undone. The main goal of KOINet is to combine Kepler data with ground-based observations in order to confirm and characterize the masses of exoplanet candidates using TTVs.

It is crucial for TTV studies to continue the work of space missions from ground. It is unlike, only with space-based observations, to cover the interaction timescales to dynamically prove the TTV signal and the existence of possible companions, as in shown in Figure \ref{koinet}. In this figure, new data from ground-based telescopes were fundamental to confirm the TTV signal, and therefore to perform a proper characterization of the system.

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{imagenes/koinet.png}
\caption{Observed minus calculated (O-C) diagram of the KOI-525b transit times, from the KOINet project. The observations from Kepler are in blue, and two different models were fitted on those data: an orbital decay model is in red, and a periodical TTV model is in green. If only Kepler data is considered, the two model could be plausible. The new ground-based observations (in pink) were essential to confirm the TTV nature of the system, discarding an orbital decay}
\label{koinet}
\end{figure}

The new space telescope Transiting Exoplanet Survey Satellite (TESS: \cite{Ricker2014}) is providing its first discoveries. The TESS observation plan divided in 13 sectors will challenge the confirmation process and characterization of possible exoplanets. During the $\sim27$ days of each sector, many candidates will not be observed enough time to confirm and characterize them. However, this special feature will provide a huge amount of new transit events of already known transiting exoplanets, specially for those with short-period. Combining the new TESS data with ground-base follow- up observations, many possible TTVs could be confirm or rule out. Moreover, \cite{Ballard2018} predicted that around 5\% of the planets discovered by TESS will exhibit measurable TTV signals, similar to Kepler’s results.

Between Sector 1 and Sector 13, TESS observed around 15\% (see Figure \ref{tess_match.pdf}) of the stars with confirmed exoplanets but not all of them will produce a transit event within the 27 days sector's duration (see Figure \ref{chap:tess}). Anyway, several complete light curves could be obtained and analyzed. TESS data are reduced by the Science Processing Operations Center (SPOC) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST) catalogue, where can be downloaded directly by anyone.

\begin{figure}
\centering
\includegraphics[width=1.0\columnwidth]{imagenes/tess_match.pdf}
\caption{Match between all the stars with confirmed exoplanets and the TESS targets from Sector 1 to Sector 13. The empty red circles correspond to the star with confirmed exoplanets distributed by its position in the sky, while the filled red circles indicate if the exoplanet has an orbital period of less than 27 days, which is the duration of one TESS sector. The black cross indicates which star was already observed by TESS. However, this does not indicate that transit light curves will be provided for sure since the orbital period of the exoplanet needs to be considered. Thus, the first year mission of TESS will provide for sure transit data of the exoplanets with filled red circle and a black cross. The zone in the sky within the big black circle corresponds to the Kepler field of view, where the bulk of discovered exoplanets are located.}
\label{match_tess}
\end{figure}

@@

Thus, for the currently and future stage of the TraMoS project, archival data -- collected since 2008 -- will be combined with the upcoming TESS data and new ground-based observations using one-meter class telescopes. The main goal of the project remains the same: refine orbital and physical parameters of exoplanetary system and search for variations in those parameters, that could suggest the presence of additional small bodies in the system. The KOINet project proved that ground-based follow-up are, in some cases, essential to complete a possible TTV signal, and therefore, to confirm or rule out variations in the transit time. During its first year of mission, TESS will supply with consecutive transit light curves from southern targets, specially from short-period planets, such as hot Jupiters. This special feature is fundamental to construct TTV curves and then, complete them from ground-based follow-up.

In the following subsections, I present a re-analysis of the TTV curves of the hot Jupiters: WASP-18b, WASP-19b and WASP-77Ab including new transit times from TESS: 45, 28, and 15 for WASP-18b, WASP-19b and WASP-77Ab respectively. In order to compute the transit time of each light curve, I used EXOFASTv2 to only fit the transit time and the flux's baseline. The remaining planetary parameters were fixed with the values from Tables \ref{wasp18}, \ref{tab:wasp19}, \ref{tab:wasp77}.

@@

The star WASP-18 was observed continuously during Sector 2 and 3 of the TESS mission, between August 22nd and October 18th, 2018. These observations provided 47 transits events of WASP-18b, but only 45 of them were complete transits, and therefore included into the TTV analysis.

@@

This value differs from the previous reported in Eq.~\ref{eq1_w18} by $0.016$ seconds, and the error was reduced to a third.

Figure \ref{wasp18_ttv} shows the extension of the TTV curve of WASP-18b considering the new data from TESS. Including these new transit times, the scatter from the linear ephemeris was reduced to 47 seconds. A possible second order fit of a hypothetical orbital decay, has a reduced chi squared of $\chi^{2}_{red}=0.35$, while the linear fit - which corresponds to the linear ephemeris - has $\chi^{2}_{red}=0.36$. Furthermore, as there is no strong evidence for an orbital decay in this system as proposed by \cite{Wilkins2017}, the simpler model should be chosen: the linear model.

@@

WASP-19 was observed during Sector 9 between February 28th and March 26th, 2019. During this time, 29 complete transit event were provided, and then considered to compute the new TTVs of WASP-19b show in Figure \ref{wasp19_ttv}. The new best fit for the orbital period P, considering a total of 88 transit times is:

@@

The previous reported value in Eq.~\ref{eq1_wasp19} is $0.007$ seconds larger.

@@

In Eq.~\ref{eq1_w77}, the value for the orbital period P is $0.01\,\rm seconds$ lower, and the scatter from the linear ephemeris was reduced to 86 seconds. The linear fit has a reduced chi squared of $\chi^2_{red}=1.03$, while a second degree polynomial has $\chi^2_{red}=0.72$. Anyway, the second order fit is highly dominated by the outlier transit time of epoch $229$ (see Figure \ref{wasp77_ttv}). After removing it, the reduced chi squared is  $\chi^2_{red}=0.37$. In all cases, the best fit correspond to the linear ephemeris.

As the previous two targets, extending the TTV curve of WASP-77Ab with transit times from TESS light curve supported the conclusion from the previous study: there is not a clear sinusoidal signal in the variations of the transit times, that could suggest a periodic TTV in WASP-77Ab. However, from the current work this target is the one with less transit time data, thus, follow-up observations would be required to confirm the no existence of close-in companions in MMR.

>>>>

With the end of the Kepler mission, thousands of possible exoplanets remain as candidates known as Kepler Objects of Interest (KOI). The Kepler Object of Interest Network (KOINet: \citep{vonEssen2018,Freuddenthal2018}) in the Northern hemisphere, is a network of ground-based telescopes performing a photometric follow-up of KOIs to continue what Kepler left undone. The main goal of KOINet is to combine Kepler data with ground-based observations to confirm and characterize the masses of exoplanet candidates using TTVs.

TTV studies must continue the work of space missions from the ground. It is unlike, only with space-based observations, to cover the interaction timescales to dynamically prove the TTV signal and the existence of possible companions, as in shown in Figure \ref{koinet}. In this figure, new data from ground-based telescopes were fundamental to confirm the TTV signal, and therefore to perform a proper characterization of the system.

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{imagenes/koinet.png}
\caption{Observed minus calculated (O-C) diagram of the KOI-525b transit times, from the KOINet project. The observations from Kepler are in blue, and two different models were fitted on those data: an orbital decay model is in red, and a periodical TTV model is in green. If only Kepler data is considered, the two models could be plausible. The new ground-based observations (in pink) were essential to confirm the TTV nature of the system, discarding an orbital decay}
\label{koinet}
\end{figure}

The new space telescope Transiting Exoplanet Survey Satellite (TESS: \cite{Ricker2014}) is providing its first discoveries. The TESS observation plan divided into 13 sectors will challenge the confirmation process and characterization of possible exoplanets. During the $\sim27$ days of each sector, many candidates will not be observed enough time to confirm and characterize them. However, this special feature will provide a huge amount of new transit events of already known transiting exoplanets, especially for those with short-period. Combining the new TESS data with ground-based follow- up observations, many possible TTVs could be confirmed or ruled out. Moreover, \cite{Ballard2018} predicted that around 5\% of the planets discovered by TESS will exhibit measurable TTV signals, similar to Kepler’s results.

Between Sector 1 and Sector 13, TESS observed around 15\% (see Figure \ref{match_tess}) of the stars with confirmed exoplanets but not all of them will produce a transit event within the 27 days sector's duration (see Figure \ref{chap:tess}). Anyway, several complete light curves could be obtained and analyzed. TESS data are reduced by the Science Processing Operations Center (SPOC) and after being processed, they are archived in the Mikulski Archive for Space Telescopes (MAST) catalog, where can be downloaded directly by anyone.

\begin{figure}
\centering
\includegraphics[width=1.0\columnwidth]{imagenes/tess_match.pdf}
\caption{Match between all the stars with confirmed exoplanets and the TESS targets from Sector 1 to Sector 13. The empty red circles correspond to the star with confirmed exoplanets distributed by its position in the sky, while the filled red circles indicate if the exoplanet has an orbital period of fewer than 27 days, which is the duration of one TESS sector. The black cross indicates which star was already observed by TESS. However, this does not indicate that transit light curves will be provided for sure since the orbital period of the exoplanet needs to be considered. Thus, the first-year mission of TESS will provide for sure transit data of the exoplanets with a filled red circle and a black cross. The zone in the sky within the big black circle corresponds to the Kepler field of view, where the bulk of discovered exoplanets are located.}
\label{match_tess}
\end{figure}

@@

Thus, for the current and future stage of the TraMoS project, archival data -- collected since 2008 -- will be combined with the upcoming TESS data and new ground-based observations using one-meter class telescopes. The main goal of the project remains the same: refine orbital and physical parameters of the exoplanetary system and search for variations in those parameters, that could suggest the presence of additional small bodies in the system. The KOINet project proved that ground-based follow-up is, in some cases, essential to complete a possible TTV signal, and therefore, to confirm or rule out variations in the transit time. During its first year of the mission, TESS will supply with consecutive transit light curves from southern targets, especially from short-period planets, such as hot Jupiters. This special feature is fundamental to construct TTV curves and then, complete them from ground-based follow-up.

In the following subsections, I present a re-analysis of the TTV curves of the hot Jupiters: WASP-18b, WASP-19b, and WASP-77Ab including new transit times from TESS: 45, 28, and 15 for WASP-18b, WASP-19b and WASP-77Ab respectively. To compute the transit time of each light curve, I used EXOFASTv2 to only fit the transit time and the flux's baseline. The remaining planetary parameters were fixed with the values from Tables \ref{wasp18}, \ref{tab:wasp19}, \ref{tab:wasp77}.

@@

The star WASP-18 was observed continuously during Sector 2 and 3 of the TESS mission, between August 22nd and October 18th, 2018. These observations provided 47 transits events of WASP-18b, but only 45 of them were complete transits, and therefore included in the TTV analysis.

@@

This value differs from the previously reported in Eq.~\ref{eq1_w18} by $0.016$ seconds, and the error was reduced to a third.

Figure \ref{wasp18_ttv} shows the extension of the TTV curve of WASP-18b considering the new data from TESS. Including these new transit times, the scatter from the linear ephemeris was reduced to 47 seconds. A possible second-order fit of a hypothetical orbital decay has a reduced chi-squared of $\chi^{2}_{red}=0.35$, while the linear fit - which corresponds to the linear ephemeris - has $\chi^{2}_{red}=0.36$. Furthermore, as there is no strong evidence for orbital decay in this system as proposed by \cite{Wilkins2017}, the simpler model should be chosen: the linear model.

@@

WASP-19 was observed during Sector 9 between February 28th and March 26th, 2019. During this time, 29 complete transit event was provided and then considered to compute the new TTVs of WASP-19b shown in Figure \ref{wasp19_ttv}. The new best fit for the orbital period P, considering a total of 88 transit times is:

@@

The previously reported value in Eq.~\ref{eq1_wasp19} is $0.007$ seconds larger.

@@

In Eq.~\ref{eq1_w77}, the value for the orbital period P is $0.01\,\rm seconds$ lower, and the scatter from the linear ephemeris was reduced to 86 seconds. The linear fit has a reduced chi-squared of $\chi^2_{red}=1.03$, while a second-degree polynomial has $\chi^2_{red}=0.72$. Anyway, the second-order fit is highly dominated by the outlier transit time of epoch $229$ (see Figure \ref{wasp77_ttv}). After removing it, the reduced chi-squared is  $\chi^2_{red}=0.37$. In all cases, the best fit corresponds to the linear ephemeris.

Like the previous two targets, extending the TTV curve of WASP-77Ab with transit times from TESS light curve supported the conclusion from the previous study: there is not a clear sinusoidal signal in the variations of the transit times, that could suggest a periodic TTV in WASP-77Ab. However, from the current work, this target is the one with less transit time data, thus, follow-up observations would be required to confirm the no existence of close-in companions in MMR.
